Refunctionalization of Abstract Abstract Machines (Functional Pearl)

### 2018-06-25 paper/paper.tex
fix interderiving

In the domain of abstract semantic artifacts, by contrast, the relations between small-step
abstract abstract machines and big-step abstract definitional interpreters, as well as the 
question of deriving one from the other, are not well studied.
One of the fundamental differences between concrete semantic artifacts and abstract semantic
artifacts is nondeterminism. In addition to ensuring termination, abstract semantic
artifacts are usually equipped with a cache of reachable states, the cache is
updated in a monotonic way and guaranteed to reach the least fixed-point eventually.
In this functional pearl, we provide a constructive answer to the question of interderiving
abstract semantic artifacts and relate AAM and ADI by presenting a series of syntactical
transformations on the program from small-step abstract abstract machines to big-step 
abstract definitional interpreters.

@@

It is worth noting that the continuation class @Kont@ is defined as a list of
frames, where a frame can be considered a reduction context in reduction semantics.
An empty list represents empty call stack; otherwise, the head frame in the list
represents the innermost context, and the reduction result of this frame will be used
to fill the ``hole'' of its following element in the list.
We represent frames using the @Frame@ class, which stores the information of a single
call-site, i.e., the information that can be used to resume the interrupted computation.
A @Frame@ constitutes a variable name @x@ to be bound later, and a control component
to which the program may resume, and its environment.

>>>>

In the domain of abstract semantic artifacts, by contrast, the relations between small-step
abstract abstract machines and big-step abstract definitional interpreters, as well as the 
question of deriving one from the other, are not well studied.
One of the fundamental differences between concrete semantic artifacts and abstract semantic
artifacts is nondeterminism. In addition to ensuring termination, abstract semantic
artifacts are usually equipped with a cache of reachable states, the cache is
updated in a monotonic way and guaranteed to reach the least fixed-point eventually.
In this functional pearl, we make a first step to answering the question of interderiving
abstract semantics artifacts, and provide a constructive answer to relate AAM and ADI 
by presenting a series of syntactical transformations on the program from small-step 
abstract abstract machines to big-step abstract definitional interpreters.

@@

It is worth noting that the continuation class @Kont@ is defined as a list of
frames, where a frame can be considered a representation of reduction context 
in reduction semantics.
An empty list represents empty call stack; otherwise, the head frame in the list
represents the innermost context, and the reduction result of this frame will be used
to fill the ``hole'' of its following element in the list.
We represent frames using the @Frame@ class, which stores the information of a single
call-site, i.e., the information that can be used to resume the interrupted computation.
A @Frame@ constitutes a variable name @x@ to be bound later, and a control component
to which the program may resume, and its environment.
